Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-18 submission5/core.tex
Fix diagram

      ~ \stackrel{\mathtt{a0}}{\objbox\objbox} ~ \stackrel{\mathtt{a1}}{\freebox\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox\sealbox}

@@

      ~ \stackrel{\mathtt{a0}}{\freebox\freebox} ~ \stackrel{\mathtt{a1}}{\freebox\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox\sealbox}

@@

  \caption{Execution of example up through the return from {\tt f}. In stack diagrams, addresses increase to the right, stack grows to the left, and boxes represent 4-byte words. \sna{Reviewer 2 found s0 and a1 confusing, as well as lack of ra a4 and a5. Priority 3.}}

@@

security class. All callee-save registers remain \(\sealed\) for all calls.
Thus, if we varied the assembly code for the example slightly so that {\tt sensitive} was stored
in a callee-save register (e.g. {\tt s0}) rather than in memory, its security class would still be \(\sealed\)
at the entry to {\tt f}.

@@

@@

For \(LTC\), the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
%taking twice as long to catch as the next longest.
taking longer to catch.

Our properties allow us to identify an enforcement mechanism as
not really stack safe, and to validate a possible fix.
\rb{
((Cache pressure discussion relevant?))
%% Unfortunately, Lazy Per-activation Tagging and Clearing
%% puts severe pressure on the tag cache, so it may not be usable in practice.
%% However, we conjecture that no lazy scheme can be fully stack safe
%% without using unique per-activation identifiers.
}

@@

\appendix

\sna{Move to section 5, cleanup. Priority 3.}

>>>>

      ~ \stackrel{\mathtt{a0}}{\objbox\objbox} ~ \stackrel{\mathtt{a4}}{\freebox\freebox}
      ~ \stackrel{\mathtt{a5}}{\freebox\freebox}

@@

      ~ \stackrel{\mathtt{a0}}{\freebox\freebox} ~ \stackrel{\mathtt{a4}}{\freebox\freebox}
      ~ \stackrel{\mathtt{a5}}{\freebox\freebox}

@@

  \caption{Execution of example up through the return from {\tt f}. In stack diagrams, addresses increase to the right, stack grows to the left, and boxes represent 4-byte words.}

@@

security class. All callee-save registers remain \(\sealed\) for all calls, so
if we varied the assembly code for the example so that {\tt sensitive} was stored
in a callee-save register (e.g. {\tt s0}) rather than in memory, its security class would still
be \(\sealed\) at the entry to {\tt f}.

@@

\sna{Cleanup. Priority 3.}

@@

For \(LTC\), the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking longer to catch.

Our properties allow us to identify an enforcement mechanism as
not really stack safe, and to validate a possible fix.

%% I don't think this discussion is relevant here
%% Unfortunately, Lazy Per-activation Tagging and Clearing
%% puts severe pressure on the tag cache, so it may not be usable in practice.
%% However, we conjecture that no lazy scheme can be fully stack safe
%% without using unique per-activation identifiers.

@@
